MATH 3610 - Project \#1

### 2015-09-27 proj1.tex

\documentclass{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{tikz}

@@

>>>>

\documentclass{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{csvsimple}
\usepackage{pgfplots}

@@

Here is a family of values of $S(t)$.
The total population and the rate of distributing vaccines are
	held constant, while each curve corresponds to a different
	value of the growth rate constant.
Each curve starts with an initial condition at 5 percent of the
	population, and the growth rate determines how many people
	overall are infected.

\paragraph{}
\pgfplotstableread[col sep = comma]{data/s.csv}\mydata
\begin{tikzpicture}
	\begin{axis}[
		legend pos = south east,
		xmin = 0,
		xmax = 6,
		ymin = 0,
		ymax = 1.3,
		ylabel = {$S(t)$ (units of total population)},
		xlabel = {$t$}
	]
	\foreach \index in {1, ..., 35} {%
		\addplot[mark=""] table[x index = {0}, y index = {\index}]{\mydata};
	}
	\addplot[mark=""] {1 - x * 0.2};
	\end{axis}
\end{tikzpicture}
\paragraph{}
